---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ghactionsOGD

<!-- badges: start -->
[![R-CMD-check](https://github.com/ogdtg/ghactionsOGD/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ogdtg/ghactionsOGD/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of ghactionsOGD is to simplify the usage of Github Actions for small-scale data retrieval processes. A typical workflow would be to scrape data from a website on a daily basis and publish it as Open Government Data (OGD). In such a scenario the packages helps the user to set up the correct GitHub Actions Workflow including setting Actions Secrets and specifying the YAML Workflow file.

Since the package is only used for setting up the workflow, it does not need to be part of your depencencies on GitHub later on.

## Installation

You can install the development version of ghactionsOGD from [GitHub](https://github.com/ogdtg/ghactionsOGD/tree/main) with:

``` r
# install.packages("devtools")
devtools::install_github("ogdtg/ghactionsOGD")
```

## Example

To create a workflow and set Actions Secrets that can be used in the R script you can use the following command. Before running the command you should have cloned the GitHub Repo to your local machine and you should run this command from within the cloned repo.

```{r example}
library(ghactionsOGD)
create_ghactions_workflow(cron = "31 2 * * *",
                          name = "Test Run",
                          env = list(ODS_KEY = Sys.getenv("ODS_KEY")),
                          scripts = "test.R")


```


First, this command will produce the file `.github/workflows/main.yml` in your working directory (e.g. your local git repository). The file looks like this:


```yaml
name: Test
'on':
  schedule:
    - cron: 31 2 * * *
  workflow_dispatch: ~
jobs:
  run_script:
    runs-on: ubuntu-latest
    steps:
      - name: Checkout Repository
        uses: actions/checkout@v4
      - name: Execute Script
        run: Rscript test.R
        env:
          ODS_KEY: ${{ secrets.ODS_KEY }}
      - name: Set up Git
        run: |-
          git config --global --add safe.directory /__w/github_test/github_test
          git config --global user.name "GitHub Actions"
          git config --global user.email "username@users.noreply.github.com"
      - name: Check if there are changes to commit
        id: changes_check
        run: |-
          git add .
          if git diff-index --quiet HEAD; then
             echo "changes=false" >>$GITHUB_OUTPUT
          else
             echo "changes=true" >> $GITHUB_OUTPUT
          fi
      - name: Commit changes
        if: ${{ steps.changes_check.outputs.changes == 'true' }}
        run: git commit -m "Automated changes by GitHub Actions"
      - name: Push changes
        if: ${{ steps.changes_check.outputs.changes == 'true' }}
        run: git push
    container: rocker/tidyverse:4.1.2
```



You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
